Dark matter halo shape in the Auriga simulations: radial dependence, time evolution and baryon disk alignment

### 2019-07-17 Document/paper.tex
edit

The second promising extension of our results deals with the shape
alignment as a function of radius.
In concordance

\citep{Debatistta08} shape aligment with respects to the disk changes
but saturates beyond the disk radius.

{\bf Comparison with other detailed simulations.}

{\bf Comparison with other statistical simulations.}

>>>>

The second promising extension of our results deals with the shape
alignment as a function of radius.
In concordance with previous results in DM only simulations we find
that the shells of halo shape are well aligned at different radii.
The surprising result we find is that in the presences of baryons
these shells twist as a function of radius.
\citep{Debattista08} found a similar effect, but only at radii smaller
than the disk radius. At radii larger than the disk radius, they find,
the dark matter shells stop twisting.
The twisting effect is robust across our sample of 30 halos. 
Also surprisingly at a radius of $0.25R_{200}\approx 56$ kpc the
alignment between the stellar disk and the dark matter halo is almost
perfect.
